\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Artyom}
\familyname{Smirnov}
\address{}{Murom, Russia}
\mobile{+7(920)944-33-40}
\email{artyom\_smirnov@icloud.com}
\homepage{http://artyom-smirnov.info}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Brief description}
\cvline{}{
  My main direction --- system development and DBMS.\newline{}
  My primary programming language --- C++.\newline{}
  I enjoy OpenSource software and tools which I use both for work and fun.
}

\section{Projects}
\subsection{C++}
\cvline{Red~Database}{
  \url{http://www.red-soft.biz/en/reddatabase_product.html}\newline{}
  Firebird DBMS fork with improved security
}

\cvline{SciDB}{
  \url{http://www.scidb.org}\newline{}
  DBMS for large-scale scientific experiments based on multi-dimensional arrays
}

\subsection{Python}
\cvline{scidb4py}{
  \url{https://github.com/artyom-smirnov/scidb4py}\newline{}
  Pure python SciDB client library implementation
}

\subsection{Pascal}
\cvline{MTDORB}{
  \url{http://sourceforge.net/projects/mtdorb/}\newline{}
  Opensource ORB for Pascal
}

\section{Experience}
\cventry
  {Oct 2013 - present}
  {Software Engineer}
  {Red Soft Corporation}
  {}{}
  {
    Development and support of Red Database}
\cventry 
  {Dec 2009 - Sep 2013}
  {Software Engineer}
  {SciDB}
  {}{}
  {Query parsing, translating and processing\newline{}
   Client tools\newline{}
   Client libraries and drivers\newline{}
   JDBC driver\newline{}
   Build system, packaging}
\cventry
  {May 2007 - Aug 2009}
  {Software Engineer}
  {Red Soft Corporation}
  {}{}
  {
    Security improvements in Red Database - fork of Firebird RDBMS\newline{}
    Porting MTDORB from Kylix to Free Pascal\newline{}
    Porting to Linux and supporting Firebird/Red Database replication utility
  }

\section{Development skills}
\subsection{Programming Languages}
\cvlanguage{C++, C, Bash}{Expert}{}
\cvlanguage{Python, Java}{Intermediate}{}
\cvlanguage{LaTeX, Pascal}{Basic}{}
\subsection{Tools}
\cvline{}{gcc, gdb, valgrind, bison, flex, cmake, git, svn, ant, maven}

\section{Computer skills}
\cvcomputer{IDE}{Eclipse, QtCreator, Xcode}{}{}
\cvcomputer{OS}{Linux (RedHat, Debian), MacOS X}{}{}

\section{Education}
\cventry
  {Sep 2004 -  Jul 2009}
  {Information Technology}
  {Murom Institute (branch) of the Vladimir State University, Murom, Russia}
  {}{}
  {Engineer}

\section{Publications}
\cvline{}{Target-oriented distributed approach for query optimization in DBMS (rus)\newline{}
Smirnov A.V. Proceedings of <<Scientific creativity of the XXI century (NC-2012)>>. 2012. \#3. Pp. 71-79.}
\cvline{}{Problems of query optimization in extensible DBMS SciDB (rus)\newline{}
Smirnov A.V. Algorithms, methods and systems of data processing. 2011. N3(18).}
\cvline{}{Distributed approach for searching in query optimizer search space (rus)\newline{}
Smirnov A.V. Algorithms, methods and systems of data processing. 2011. \#3(18).}
\cvline{}{Dynamically extensible query optimizer (rus)\newline{}
Smirnov A.V., Pugin E.V. Proceedings of <<Problems of informatics and modelling (PIM-2011)>>. 2011. P. 69.}
\cvline{}{SciDB - new DBMS for big size of scientific data (rus)\newline{}
Oleg Bartunov, Pavel Velikhov, Roman Simakov, Konstantin Knizhnik, Artyom Smirnov. Supercomputers journal. \#5(15). Moscow. 2011.}
\cvline{}{Overview of SciDB: Large Scale Array Storage, Processing and Analysis (eng)\newline{}
J. Rogers, R. Simakov, E. Soroush, P. Velikhov, M. Balazinska, D. DeWitt, B. Heath, D. Maier, S. Madden, J. Patel, M. Stonebraker, S. Zdonik, A. Smirnov, K. Knizhnik, Paul G. Brown SIGMOD 2010}
\cvline{}{The control of access to system catalog in DBMS <<Red Database>> (rus)\newline{}
Roman Simakov, Artyom Smirnov. Information security of regions journal. \#1(4). pp. 62-66. Saratov. 2009.}
\cvline{}{Development of query optimizer model (rus)\newline{}
Smirnov A.V., Pugin E.V. Algorithms, methods and systems of data processing. 2010. \#15. Pp. 161-169.}
\cvline{}{Specifics of data distribution in multidimensional DBMS SciDB (rus)\newline{}
Smirnov A.V., Andrianov D.E. Algorithms, methods and systems of data processing. 2009. \#14. Pp. 158-163.}


\section{Links}
\cvline{Personal~page}{\url{http://www.artyom-smirnov.info/}}
\cvline{LinkedIn}{\url{http://www.linkedin.com/in/artyomsmirnov}}
\cvline{GitHub}{\url{https://github.com/artyom-smirnov}}

\end{document}
